---
title: "AdobeAPITemplate"
output: html_document
---

#*PRE-FACE
API Package Documentation <https://cran.r-project.org/web/packages/RSiteCatalyst/RSiteCatalyst.pdf>

HOW TO RUN THE CODE: Gray code chunks can be run using the respective green arrow on the right, individual or highlighted lines can be run by pressing ctrl + enter with row highlighted or cursor in row.

'<-' indicates assigning a value to an item/variable to use later. Defined variables will be found in the 'Environment' window.
ExampleVariable <- 'definition of example'

#1. API AUTHENTICATION & RSITECATALYST PACKAGE

```{r 1st Time Package Install}
#install.packages('RSiteCatalyst')
#install.packages('readr')
```

To obtain authentication credentials (may need to ask a user with access):
1. Log in to Adobe Analytics: <https://my.omniture.com/login/>
2. In the 'Admin' dropdown, select 'Company Settings'
3. Select 'Web Services'
4. Locate your 'Web Services Username' and 'Shared Secret'
*MUST ADD YOUR USERNAME AND SHARED SECRET FOR SCRIPT TO WORK

```{r Initiate Library & Authentication}
library(RSiteCatalyst)
library(readr) #load this if you want to read/write CSVs and keep the header intact

WebServicesUsername <- 'yourusernamehere'
SharedSecret <- 'yoursharesecrethere'

SCAuth(WebServicesUsername, SharedSecret)
```

#Available Report Suites

View all available report suites

```{r Report Suites}
AvailableRSIDs <- GetReportSuites()
View(AvailableRSIDs)
```

#2. SET REPORT SUITE
Set RSID equal to the report suite id that you would like to retrieve data for

```{r Define Report Suite}
RSID <- 'vrs_rcci1_excaliburproductionm'
```

#Available Context Data For Report Suite
View available elements for defined report suite

```{r Reference Context Data}
AvailableMetrics <- GetMetrics(RSID) #includes standard metrics, custom metrics, calculated metrics
View(AvailableMetrics)

AvailableSegments <- GetSegments(RSID)
View(AvailableSegments)

AvailableElements <- GetElements(RSID) #eVars, Props, other dimensions
View(AvailableElements)
```

#3. SET REPORT PARAMETERS

*Define elements to be included in the report
*Standard, event, and calculated metrics supported
*Maximum dimensions - 4
*If multiple segments are included below, they will be treated as an 'AND' condition (ex. Segment 1: Brand ID = CEL & Segment 2: Ship Code = AL, would yield 0 results as AL is RCI)

```{r Define Report Elements}
ReportMetrics <- c('pageviews','cm300006910_5dd83c4f53953069b28e109d')
ReportDimensions <- c('evar139')
DateFrom <- '2020-03-15'
DateTo <- Sys.Date()-1
ReportSegments <- c('s300006910_5a660d9c8b49b744fc6d10b2')
DateGranularity <- 'day' #select from 'hour','day','week','month','year'
MaxRequestTime <- 10 #in minutes

#Don't Touch
IntervalSeconds <- 5
MaxIntervals <- (MaxRequestTime * 60) / IntervalSeconds
```

#4. REQUEST REPORT

Report Types:
A.TRENDED REPORT - 1 or more elements with date granularity (ex. visits by device by day)
B.RANKED REPORT - 1 or more elements with no date granularity (ex. visits by device)
C.OVERTIME REPORT - No elements with date granularity (ex. visits by day)
D.SUMMARY REPORT - No elements with no date granularity (ex. visits for a specified period of time) *Cannot apply segments

Once the code is executed, the API will send requests for the specified report to Adobe until the report is ready and received (default of 10 min request window - 120 attempts at 5 sec interval).

#a. Trended Report
```{r A.Run Trended Report}
API_Pull <- QueueTrended(reportsuite.id = RSID,
                         metrics = ReportMetrics,
                         elements = c(ReportDimensions,'evar143'),
                         date.to = DateTo,
                         date.from = DateFrom,
                         date.granularity = DateGranularity,
                         segment.id = ReportSegments,
                         max.attempts = MaxIntervals,
                         interval.seconds = IntervalSeconds,
                         top = 50000)

View(API_Pull)
```

#b. Ranked Report
A date column is not included in the ranked report. To keep track of date ranges, add DateFrom & DateTo variable values as columns after running the pull.
```{r B.Run Ranked Report}
API_Pull <- QueueRanked(reportsuite.id = RSID,
                        metrics = ReportMetrics,
                        elements = ReportDimensions,
                        date.to = DateTo,
                        date.from = DateFrom,
                        segment.id = ReportSegments,
                        max.attempts = MaxIntervals,
                        interval.seconds = IntervalSeconds,
                        top = 50000)
API_Pull$DateFrom <- DateFrom
API_Pull$DateTo <- DateTo

View(API_Pull)
```

#c. Overtime Report
The overtime report includes columns that are not necessarily useful (name, year, month, day). Remove by uncommenting '<- NULL' lines.
```{r C.Run Overtime Report}
API_Pull <- QueueOvertime(reportsuite.id = RSID,
                         metrics = ReportMetrics,
                         date.to = DateTo,
                         date.from = DateFrom,
                         date.granularity = DateGranularity,
                         segment.id = ReportSegments,
                         max.attempts = MaxIntervals,
                         interval.seconds = IntervalSeconds)

#API_Pull$name <- NULL
#API_Pull$year <- NULL
#API_Pull$month <- NULL
#API_Pull$day <- NULL

View(API_Pull)
```

#d. Summary Report
Summary report includes an unpleasant date range field. Similar to ranked, add DateFrom & DateTo fields
```{r D.Run Summary Report}
API_Pull <- QueueSummary(reportsuite.id = RSID,
                         metrics = ReportMetrics,
                         date.to = DateTo,
                         date.from = DateFrom,
                         max.attempts = MaxIntervals,
                         interval.seconds = IntervalSeconds)

API_Pull$DateFrom <- DateFrom
API_Pull$DateTo <- DateTo
API_Pull$period <- NULL

View(API_Pull)
```

#REPORT TIPS
These are ways to get around a few limitations with the API

A.MORE THAN 50K RECORD BREAKDOWN - Loop through top N results with different start points until no data is retrieved
B.SEPARATE SEGMENTS - Loop through a segment list to get results by segment without treating them as 'AND' logic
C.CUSTOM DATE INTERVALS - Each loop is individual pulled by a date chunk using your own series parameters
D.RENAME CALCULATED METRICS - Calculated metric ids are annoying, let's rename them dynamically
E.QUEUE LARGE REPORTS - Avoid waiting for excessive API requests

#a. For Breakdowns w/More Than 50K Records
Use a loop to bypass API request limitation of 50K records

```{r Set 50K+ Loop Parameters}
count.limit <- 1000000  #the max number of records we're interested in
count.step <- 20000 #how many records to retrieve per request, must not exceed 50k
count.start <- 1 #which record number to start with
```

Loop runs count.step results, saves results in a temporary table that is then appended to the final table on each loop.

```{r Run Trended 50K+ Report With Loop}
API_Pull <- NULL

for(i in seq(1, count.limit, by = count.step)) {
  print(paste("Requesting rows",i, "through", i + count.step - 1))
  
  
  Temp_API_Pull <- QueueTrended(RSID,
                                date.from = DateFrom,
                                date.to = DateTo,
                                max.attempts = MaxIntervals,
                                top = count.step,
                                start = i,
                                date.granularity = DateGranularity,
                                segment.id = ReportSegments,
                                metrics = ReportMetrics,
                                elements = ReportDimensions)
  
  
  if  (nrow(Temp_API_Pull) == 0 ) {   # no more rows were returned - presumably we have them all now
    print("Last batch had no rows, exiting loop")
    break
  }
  
  Temp_API_Pull$batch.start.row <- i
  
  API_Pull <- rbind(API_Pull, Temp_API_Pull)
  
}

View(API_Pull)
```

#b. For Separate Reports by Segment
Use a loop to repeat the same report for multiple segments (ex. iOS, Android ) and append data sets

```{r Set Segment Loop Parameters}
SegmentLoop <- list('s300006910_5b7449743f1e927f820e94a6','s300006910_5b744917d39bbd686b35d8bd')
```

Loop runs through the segment list, saves results in a temporary table that is then appended to the final table on each loop. MUST RUN SEGMENT LOOP FIRST

```{r Run Trended Segment Report With Loop}
API_Pull <- NULL

for(seg in SegmentLoop) {
  print(paste("Requesting segment:",seg))
  
  
  Temp_API_Pull <- QueueTrended(RSID,
                                date.from = DateFrom,
                                date.to = DateTo,
                                max.attempts = MaxIntervals,
                                interval.seconds = IntervalSeconds,
                                date.granularity = DateGranularity,
                                segment.id = c(seg, ReportSegments),
                                metrics = ReportMetrics,
                                elements = ReportDimensions)
  
  API_Pull <- rbind(API_Pull, Temp_API_Pull)
}

View(API_Pull)
```

#c. For Custom Date Intervals

```{r Run Custom Date Interval Report With Loop}
API_Pull <- NULL

week <- seq(from=as.Date(DateFrom), to=as.Date(DateTo),by=7 ) #based on start date +7 day increments

date1 <- NULL
date2 <- NULL

for ( i in seq_along(week)){
  date1 <- week[i]
  date2 <- date1 + 6
  print(paste("Requesting date ",date1," through ",date2))
  
  Temp_API_Pull <- QueueRanked(reportsuite.id = RSID,
                        metrics = ReportMetrics,
                        elements = ReportDimensions,
                        date.to = date2,
                        date.from = date1,
                        segment.id = ReportSegments,
                        max.attempts = MaxIntervals,
                        interval.seconds = IntervalSeconds,
                        top = 50000)
  
  Temp_API_Pull$DateFrom <- date1
  Temp_API_Pull$DateTo <- date2
  
  API_Pull <- rbind(API_Pull, Temp_API_Pull)
}

View(API_Pull)
```

#d. If you used calculated metrics in your report, let's rename those
Use a loop to rename calculated metrics to friendly names

```{r Rename Metric IDs}
for (metric_id in ReportMetrics){
  names(API_Pull)[names(API_Pull) == metric_id] <- AvailableMetrics[AvailableMetrics$id == metric_id, 'name']
}

View(API_Pull)
```

#e. If you don't want to wait for API requests, retrieve report later
Set the report to EnqueuOnly = TRUE
Created report ID is good ~48 hours

```{r Run Trended Report with EnqueueOnly = TRUE}
API_Pull_ID <- QueueTrended(reportsuite.id = RSID,
                         metrics = ReportMetrics,
                         elements = ReportDimensions,
                         date.to = DateTo,
                         date.from = DateFrom,
                         date.granularity = DateGranularity,
                         segment.id = ReportSegments,
                         max.attempts = MaxIntervals,
                         interval.seconds = IntervalSeconds,
                         enqueueOnly = TRUE,
                         top = 50000)
```

Retrieve API Pull by ID
```{r Get Report by API Pull ID}
API_Pull <- GetReport(API_Pull_ID)
```

#5. OUTPUT DATA
A.TO CSV - write to a specified file path

```{r A.To CSV}
write_csv(API_Pull,'DemoAPI.csv')
```